Suppose
\[
    \mathscr{A}_{MN} =
    \begin{pmatrix}
        1 & \cdots & 1 \\
        \vdots & \ddots & \vdots \\
        1 & \cdots & 1
    \end{pmatrix} - \mathscr{B}
    \]
is a~\( N\times N \) matrix composed of
\( N^2 - M \) unities and \( M \) zeroes.
If considered as an adjacency matrix \( \mathscr{A}_{MN} \)
defines a~complete digraph with loops on \( N \) vertices
with some \( M \) out of \( N^2 \) total edges removed.
Some important properties of a~graph are determined by its spectrum.
For example Wang et al. \cite{epidemic} proposed a~discrete-time model
of viral propagation in a~network.
In that model a virus will die out or linger on
depending on whether the ratio of curing and infection rates
is below or above the treshold value.
Wang et al. have shown that treshold value
to be the spectral radius of the adjacency matrix of the network,
i.e. the largest absolute value of its eigenvalues.
More comprehensive description of spectral graph theory
and its application is given by Cv\`etkovic et al. \cite{cvet}.

This article analyzes spectral properties of such matrices.
The matrix \( \mathscr{A}_{MN} \) can be represented in the form
\( \mathscr{A}_{MN} = \mathcal{J}_N - \mathscr{B}_{MN} \),
where \( \mathcal{J}_N \) is a~\( N\times N \) matrix
whose all entries are ones
and \( \mathcal{B}_{MN} \) has unities exactly at these \( M \)
places where \( \mathscr{A}_{MN} \) has zeroes.
The spectrum of \( \mathcal{J}_N \) can be easily computed:
\( \mathcal{J}_N^2 = N \mathcal{J} \),
so \( \lambda(\lambda - N) \) is the minimal
annihilating polynomial of \( \mathcal{J}_N \)
and hence the spectrum of \( \mathcal{J}_{N} \) is
\( \sigma(\mathcal{J}_N) = \{ 0,N \} \).

If the \( M \) is small enough, then the eigenvalues of \( \mathscr{A}_{MN} \)
should be ``close'' to those of \( \mathcal{J}_N \).
The method of similar operators \cite{baskakov-harmonic,baskakov-split} is used
to prove the following
\begin{thm}\label{kozlukovsv:thm:almost-all-ones}
    Let \( M < \frac{N^2}{16} \),
    then the spectrum of \( \mathscr{A}_{MN} \) can be represented as a~disjoint union
    \( \sigma\left(\mathscr{A}_{MN}\right) = \sigma_1 \cup \sigma_2 \)
    of a~singletone \( \sigma_1=\{\lambda_1\} \)
    and the set \( \sigma_2 \), satisfying the following conditions:
    \[
        \sigma_1 \subset \left\{
            \mu\in\mathbb{R}; %\lvert \mu - N \rvert < 4\sqrt{M}
            \right\},
        \]
    \[ \sigma_2 \subset \left\{ \mu\in\mathbb{C}; \lvert \mu \rvert < 4\sqrt{M} \right\}. \]
\end{thm}

