Let \( \mathscr{A}_{MN} \) be a \( N\times N \) matrix composed of
\( N^2 - M \) unities and \( M \) zeroes.
Considered as an adjacencies matrix \( \mathscr{A}_{MN} \)
corresponds to a complete digraph with loops on \( N \) vertices
with some \( M \) out of \( N^2 \) edges removed.
Some important properties of a graph are determined by its spectrum.
For example Wang et al. \cite{epidemic} proposed a discrete-time model
of viral propagation in a network.
In that model the virus will die out or linger on
depending on whether the ratio of curing and infection rates
is below or above the treshold value.
As Wang et al. have shown that treshold value
is the spectral radius of the adjacencies matrix of the network graph,
i.e. the maximal absolute value of its eigenvalues.
More comprehensive description of spectral graph theory
and its application is given by Cv\`etkovic et al. \cite{cvet}.

This article analyzes spectral properties of such matrices.
The matrix \( \mathscr{A}_{MN} \) can be represented in the form
\( \mathscr{A}_{MN} = \mathcal{J}_N - \mathscr{B}_{MN} \),
where \( \mathcal{J}_N \) is a \( N\times N \) matrix
whose all entries are ones
and \( \mathcal{B}_{MN} \) has unities exactly at these \( M \)
places where \( \mathscr{A}_{MN} \) has zeroes.
The spectrum of \( \mathcal{J}_N \) can be easily computed:
\( \mathcal{J}_N^2 = N \mathcal{J} \),
so \( \lambda(\lambda - N) \) is the minimal
annihilating polynomial of \( \mathcal{J}_N \)
and hence the spectrum of \( \mathcal{J}_{N} \) is
\( \sigma(\mathcal{J}_N) = \{ 0,N \} \).

For small enough \( M \) the eigenvalues of \( \mathscr{A}_{MN} \)
will be ``close'' to those of \( \mathcal{J}_N \).
Then The Method of Similar Operators \cite{baskakov-harmonic,baskakov-split} is used,
which allows in the case of perturbation of some ideal object (whose properties are known)
to find an element of algebra under consideration similar to disturbed one
yet having ``simpler'' structure.
Via this method the following theorem is proven:
%\textbf{Theorem.}
\begin{center}
\it
    Let \( M < \frac{N^2}{16} \),
    then the spectrum of \( \mathscr{A}_{MN} \) can be represented as a disjoint union
    \( \sigma\left(\mathscr{A}_{MN}\right) = \sigma_1 \cup \sigma_2 \)
    of a singletone \( \sigma_1=\{\lambda_1\} \)
    and the set \( \sigma_2 \), satisfying the following conditions:
    \[ \sigma_1 \subset \left\{ \mu\in\mathbb{R}; \lvert \mu - N \rvert < 4\sqrt{M} \right\}, \]
    \[ \sigma_2 \subset \left\{ \mu\in\mathbb{C}; \lvert \mu \rvert < 4\sqrt{M} \right\}. \]
\end{center}
